Exoplanet population inference and the rate of Earth analogs \\ from noisy, incomplete catalogs

### 2014-06-09 document/ms.tex
mentioning that our results are different

Our constraint on the rate density of Earth analogs (as defined in
\sect{extrap}) is in tension---even though our result has large fractional
uncertainty---with the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
probability function for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate density of Earth analogs is
\begin{eqnarray}
\gammaearth &=& 0.017^{+0.018}_{-0.009}~\densityunit
\end{eqnarray}
where the ``\densityunit'' indicates that this quantity is a rate density, per
natural logarithmic period per natural logarithmic radius.
Converted to these units, \citet{petigura} measured
$0.119_{-0.046}^{+0.035}~\densityunit$ for the same quantity (indicated as the
vertical lines in \fig{real-rate}).
This rate density is \emph{exactly} what Petigura's extrapolation model
predicts but, for comparison, we can also integrate our inferred rate density
over their choice of ``Earth-like'' bin ($200 \le \period/\mathrm{day} < 400$
and $1 \le \radius/\radius_\oplus < 2$) to find a \emph{rate} of
Earth-analogs.
The published rate is $0.057_{-0.017}^{+0.022}$ (\citealt{petigura}) and our
posterior constraint is
\begin{eqnarray}
\int_{\period=200\,\mathrm{day}}^{400\,\mathrm{day}}
\int_{\radius=1\,\radius_\oplus}^{2\,\radius_\oplus}
\rate_\ratepars (\ln\period,\,\ln\radius)
\dd[\ln\radius]
\dd[\ln\period]
&=&
0.016_{-0.007}^{+0.011}
\quad.
\end{eqnarray}

>>>>

Our constraint on the rate density of Earth analogs (as defined in
\sect{extrap}) is in tension---even though our result has large fractional
uncertainty---with the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
probability function for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate density of Earth analogs is
\begin{eqnarray}\eqlabel{ge-result}
\gammaearth &=& 0.017^{+0.018}_{-0.009}~\densityunit
\end{eqnarray}
where the ``\densityunit'' indicates that this quantity is a rate density, per
natural logarithmic period per natural logarithmic radius.
Converted to these units, \citet{petigura} measured
$0.119_{-0.046}^{+0.035}~\densityunit$ for the same quantity (indicated as the
vertical lines in \fig{real-rate}).
This rate density is \emph{exactly} what Petigura's extrapolation model
predicts but, for comparison, we can also integrate our inferred rate density
over their choice of ``Earth-like'' bin ($200 \le \period/\mathrm{day} < 400$
and $1 \le \radius/\radius_\oplus < 2$) to find a \emph{rate} of
Earth analogs.
The published rate is $0.057_{-0.017}^{+0.022}$ (\citealt{petigura}) and our
posterior constraint is
\begin{eqnarray}
\int_{\period=200\,\mathrm{day}}^{400\,\mathrm{day}}
\int_{\radius=1\,\radius_\oplus}^{2\,\radius_\oplus}
\rate_\ratepars (\ln\period,\,\ln\radius)
\dd[\ln\radius]
\dd[\ln\period]
&=&
0.016_{-0.007}^{+0.011}
\quad.
\end{eqnarray}

Our inferred rate density of Earth analogs (\eqalt{ge-result}) is not
consistent with the previously published result even though we use
\emph{exactly the same dataset}.
This inconsistency is due to the different assumptions made.
In particular, for their analysis, \citet{petigura} asserted that the period
distribution for small planets on long orbits is flat in logarithmic period.
If we enforce the same constraint, we reproduce their result but we relax this
assumption, allowing the data to constrain the period distribution, we find
evidence for a \emph{decreasing} period distribution as a function of
logarithmic period (see \fig{period}).
